INSTRUCTIONS TO PREPARE A FULL PAPER FOR THE 9th EUROPEAN CONGRESS ON COMPUTATIONAL METHODS IN APPLIED SCIENCES AND ENGINEERING\break ECCOMAS CONGRESS 2024

### 2024-03-13 paper/paper.tex
paper: all paths relative to ROOT

@@

\begin{figure}
    \begin{center}
        \includegraphics[width=0.95\textwidth]{../figures/beam/beam_sketch.pdf}
    \end{center}
    \caption{Schematic representation of the structural problem. A simply supported beam is subjected to a constant load.}\label{fig:beam_sketch}
\end{figure}

% TODO placement
\begin{figure}
    \begin{center}
        \includegraphics[width=0.65\textwidth]{../figures/beam/unit_cell.png}
    \end{center}
    \caption{Unit cell domain partition.}\label{fig:unit_cell_domain}
\end{figure}

\begin{figure}
    \begin{center}
        \includegraphics[width=0.95\textwidth]{../figures/beam/global_domain.png}
    \end{center}
    \caption{The partition of the global domain. The colors indicate the variation in Young's modulus for each subdomain.}\label{fig:global_domain}
\end{figure}

@@

\begin{figure}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{../figures/beam/fig_loc_svals_left.pdf}
  \caption{Singular valus left}\label{fig:loc_svals_left}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{../figures/beam/fig_loc_svals_inner.pdf}
  \caption{Singular valus inner}\label{fig:loc_svals_inner}
\endminipage\hfill
\minipage{0.32\textwidth}%
  \includegraphics[width=\linewidth]{../figures/beam/fig_loc_svals_right.pdf}
  \caption{Singular valus right}\label{fig:loc_svals_right}
\endminipage
\end{figure}

@@

\begin{figure}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{../figures/beam/fig_proj_error_left_hapod.pdf}
  \caption{Projection error hapod}\label{fig:proj_error_left_hapod}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{../figures/beam/fig_proj_error_inner_hapod.pdf}
  \caption{Projection error hapod}\label{fig:proj_error_inner_hapod}
\endminipage\hfill
\minipage{0.32\textwidth}%
  \includegraphics[width=\linewidth]{../figures/beam/fig_proj_error_right_hapod.pdf}
  \caption{Projection error hapod}\label{fig:proj_error_right_hapod}
\endminipage
\end{figure}

@@

\begin{figure}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{../figures/beam/fig_proj_error_left_heuristic.pdf}
  \caption{Projection error }\label{fig:proj_error_left_heuristic}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{../figures/beam/fig_proj_error_inner_heuristic.pdf}
  \caption{Projection error }\label{fig:proj_error_inner_heuristic}
\endminipage\hfill
\minipage{0.32\textwidth}%
  \includegraphics[width=\linewidth]{../figures/beam/fig_proj_error_right_heuristic.pdf}
  \caption{Projection error }\label{fig:proj_error_right_heuristic}
\endminipage
\end{figure}

@@

\begin{figure}[!htb]
    \includegraphics[width=\linewidth]{../figures/beam/fig_loc_rom_error.pdf}
    \caption{A really Awesome Image}\label{fig:loc_rom_error}
\end{figure}

>>>>

\usepackage{standalone}
\usepackage{booktabs}
\usepackage{pgfplotstable}
\pgfplotsset{compat=1.18}

@@

\begin{figure}
    \begin{center}
        \includegraphics[width=0.95\textwidth]{./figures/beam/beam_sketch.pdf}
    \end{center}
    \caption{Schematic representation of the structural problem. A simply supported beam is subjected to a constant load.}\label{fig:beam_sketch}
\end{figure}

% TODO placement
\begin{figure}
    \begin{center}
        \includegraphics[width=0.65\textwidth]{./figures/beam/unit_cell.png}
    \end{center}
    \caption{Unit cell domain partition.}\label{fig:unit_cell_domain}
\end{figure}

\begin{figure}
    \begin{center}
        \includegraphics[width=0.95\textwidth]{./figures/beam/global_domain.png}
    \end{center}
    \caption{The partition of the global domain. The colors indicate the variation in Young's modulus for each subdomain.}\label{fig:global_domain}
\end{figure}

@@

\begin{figure}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{./figures/beam/fig_loc_svals_left.pdf}
  \caption{Singular valus left}\label{fig:loc_svals_left}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{./figures/beam/fig_loc_svals_inner.pdf}
  \caption{Singular valus inner}\label{fig:loc_svals_inner}
\endminipage\hfill
\minipage{0.32\textwidth}%
  \includegraphics[width=\linewidth]{./figures/beam/fig_loc_svals_right.pdf}
  \caption{Singular valus right}\label{fig:loc_svals_right}
\endminipage
\end{figure}

@@

\begin{figure}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{./figures/beam/fig_proj_error_left_hapod.pdf}
  \caption{Projection error hapod}\label{fig:proj_error_left_hapod}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{./figures/beam/fig_proj_error_inner_hapod.pdf}
  \caption{Projection error hapod}\label{fig:proj_error_inner_hapod}
\endminipage\hfill
\minipage{0.32\textwidth}%
  \includegraphics[width=\linewidth]{./figures/beam/fig_proj_error_right_hapod.pdf}
  \caption{Projection error hapod}\label{fig:proj_error_right_hapod}
\endminipage
\end{figure}

\begin{table}
    \caption{HAPOD inner}\label{tab:hapod_inner}
    \input{./src/beam/tables/hapod_inner.tex}
\end{table}

@@

\begin{figure}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{./figures/beam/fig_proj_error_left_heuristic.pdf}
  \caption{Projection error }\label{fig:proj_error_left_heuristic}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{./figures/beam/fig_proj_error_inner_heuristic.pdf}
  \caption{Projection error }\label{fig:proj_error_inner_heuristic}
\endminipage\hfill
\minipage{0.32\textwidth}%
  \includegraphics[width=\linewidth]{./figures/beam/fig_proj_error_right_heuristic.pdf}
  \caption{Projection error }\label{fig:proj_error_right_heuristic}
\endminipage
\end{figure}

\begin{table}
    \caption{Heuristic rrf inner}\label{tab:heuristic_inner}
    \input{./src/beam/tables/heuristic_inner.tex}
\end{table}

@@

\begin{figure}[!htb]
    \includegraphics[width=\linewidth]{./figures/beam/fig_loc_rom_error.pdf}
    \caption{A really Awesome Image}\label{fig:loc_rom_error}
\end{figure}
